### 2021-02-16 abstract.tex
Correct a typo: amount > ammount
Remove commented-out content from abstract

% The state-of-the-art \acrlongpl{atp} for \acrlong{fol}, such as Vampire,
State-of-the-art superposition-based theorem provers for \acrlong{fol} % such as E or Vampire,
% - imho sem patri neurcity clen (the 0 clen v mnoznem cisle)
% - byl specifictejsi z vymezenim katergorie dokazovacu
% - to ``such as'' bych pripadne vynechal
% use \glspl{sot} to constrain the proof search.
rely on \glspl{sot} to constrain the applicability of inference rules 
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
a \emph{symbol precedence}---a permutation of the predicate and function symbols
% occurring in the input problem.
% maybe:
of the input problem's signature.
The choice of the precedence thus has an indirect yet often substantial impact 
% on the length of the proof search.
on the ammount of work required to successfully complete a proof search.

@@

This paper describes and evaluates a symbol precedence recommender,
a machine learning system which estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology % \acrlong{gcn} % how to put neural in the middle?
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.

% When trained on proof attempts that use random symbol precedences,
% the recommender outperforms the state-of-the-art heuristic by more than \SI{2}{\percent}.
% The recommender is evaluated on \acrlong{fol} problems from the \acrshort{tptp} problem library.
% \todo{FB: Should I mention Vampire here?}
% \todo{FB: Try to mention that the recommender is signature-agnostic.}

@@

\keywords{saturation-based theorem proving \and
% \gls{sot} \and
simplification ordering \and % isn't it great to be sometimes able to say ``simplification ordering on terms'' and sometimes just "simplification ordering"?
symbol precedence \and
\acrlong{ml} \and
\acrlong{gcn}}

>>>>

State-of-the-art superposition-based theorem provers for \acrlong{fol}
rely on \glspl{sot} to constrain the applicability of inference rules 
which in turn shapes the ensuing search space.
The popular Knuth-Bendix simplification ordering is parameterized by 
a \emph{symbol precedence}---a permutation of the predicate and function symbols
of the input problem's signature.
The choice of the precedence thus has an indirect yet often substantial impact 
on the amount of work required to successfully complete a proof search.

@@

This paper describes and evaluates a symbol precedence recommender,
a machine learning system which estimates the best possible precedence
based on observations of prover performance on a set of problems and random precedences.
Using the graph convolutional neural network technology
the system does not presuppose the problems to be related or share a common signature. 
When coupled with the theorem prover Vampire and evaluated on the \acrshort{tptp} problem library
the recommender is found to outperform a state-of-the-art heuristic by more than \SI{2}{\percent}.

@@

\keywords{saturation-based theorem proving \and
simplification ordering \and
symbol precedence \and
\acrlong{ml} \and
\acrlong{gcn}}
